---
title: "vbhavya_PeerCommentary_julid24_05"
author: "Bhavya Deepti Vadavalli"
date: "`r Sys.Date()`"
output: 
  html_document:
    theme: cerulean
    toc: yes
    toc_float: true
---
```{r}
library(curl)
data <- curl("https://raw.githubusercontent.com/fuzzyatelin/fuzzyatelin.github.io/master/AN588_Fall23/KamilarAndCooperData.csv")
kc <- read.csv(data, header = TRUE, stringsAsFactors = FALSE)
attach(kc)
```

# Problem 1 Beta Coefficients
> Using the “KamilarAndCooperData.csv” dataset, run a linear regression looking at log(HomeRange_km2) in relation to log(Body_mass_female_mean) and report your β coeffiecients (slope and intercept).

```{r}
# Fit the model
# x = log(Body_mass_female_mean)
# y = log(HomeRange_km2)
kc_fit <- lm(log(HomeRange_km2)~log(Body_mass_female_mean))
summary(kc_fit)
coef(kc_fit)
```

# Problem 2 Bootstrapping
>Then, use bootstrapping to sample from your data 1000 times with replacement, each time fitting the same model and calculating the same coefficients. This generates a sampling distribution for each β coefficient.

```{r}
# Bootstrapping for β coefficients
# reference source: https://www.statmethods.net/advstats/bootstrapping.html 
library(boot)
data <- data.frame(kc)

reg_boot <- function(data, idx) {
  fit <- lm(log(HomeRange_km2)~log(Body_mass_female_mean), data=data[idx, ])
  coef(fit)
} 

b <- boot(data, reg_boot, 1000)
b_coefs <- b$t
print(b_coefs)
# not entirely sure if this is right but I tried so many other things that didn't work and this kinda looks like it worked.

#vbhavya: Hey. I'm glad you could figure it out. Maybe you could explain the function a bit. I didn't do it this way so I guess I just think it could help anyone else looking at the code understand it better.  
```

> Estimate the standard error for each of your β coefficients as the standard deviation of the sampling distribution from your bootstrap and determine the 95% CI for each of your β coefficients based on the appropriate quantiles from your sampling distribution.

```{r}
library(boot)
se_b <- apply(b_coefs, 2, sd)
print(se_b)
```

```{r}
ci_b <- boot.ci(b, index=1, type="perc")
print(ci_b)
```

> How does the former compare to the SE estimated from your entire dataset using the formula for standard error implemented in lm()?

> Answer: They SEs are pretty close in number. The SE from the entire dataset is slightly greater than the SE from the bootstrap data.

```{r}
# SE estimated from entire dataset
se_data <- summary(kc_fit)
se_data

# SE from bootstrap data
se_b <- apply(b_coefs, 2, sd)
print(se_b)
```

> How does the latter compare to the 95% CI estimated from your entire dataset?

> Answer: They are pretty close in number.

```{r}
# CI from entire dataset
CI_data <- confint(kc_fit)
CI_data

# CI from bootstrap data
ci_b <- boot.ci(b, index=1, type="perc")
print(ci_b)
```


# Extra Credit
> Write a FUNCTION that takes as its arguments a dataframe, “d”, a linear model, “m” (as a character string, e.g., “logHR~logBM”), a user-defined confidence interval level, “conf.level” (with default = 0.95), and a number of bootstrap replicates, “n” (with default = 1000). Your function should return a dataframe that includes: beta coefficient names; beta coefficients, standard errors, and upper and lower CI limits for the linear model based on your entire dataset; and mean beta coefficient estimates, SEs, and CI limits for those coefficients based on your bootstrap.

```{r}
# Create empty function
bootstrap_lm <- function(d, m, conf.level = 0.95, n = 1000) {

# "m" as a character string e.g., "logHR~logBM"
string <- as.formula(m)
  
# Fit the linear model 
model <- lm(string, data = d)
  
# Beta coefficients and standard errors
beta_coef <- coef(model)
se_coef <- summary(model)$coef[, "Std. Error"]
  
# Create an empty matrix to store bootstrap results
bootstrap_results <- matrix(NA, nrow = n, ncol = length(beta_coef))
  
# Perform bootstrap
  for (i in 1:n) {
# Sample with replacement from the original data
    sampled_data <- d[sample(nrow(d), replace = TRUE), ]
    
# Fit a linear model on sample data input by user
    sampled_model <- lm(string, data = sampled_data)
    
# Store the beta coefficients for the bootstrap samples
    bootstrap_results[i, ] <- coef(sampled_model)
  }
  
# Calculate confidence intervals
  alpha <- (1 - conf.level) / 2
  lower_ci <- apply(bootstrap_results, 2, function(x) quantile(x, alpha))
  upper_ci <- apply(bootstrap_results, 2, function(x) quantile(x, 1 - alpha))
  
# List Results
  result_df <- data.frame(
    Coefficient = names(beta_coef),
    Estimate = beta_coef,
    SE = se_coef,
    Lower_CI = lower_ci,
    Upper_CI = upper_ci
  )
  
  return(result_df)
}

#vbhavya: It's really cool that you did the extra-credit. I really liked how you broke the steps up and it was really easy to follow!
```

```{r}
# Test
bootstrap_lm(kc, log(HomeRange_km2)~log(Body_mass_female_mean), conf.level=0.95, n=1000)
```

# Challenges
> I didn't find this hw too challenging because it combined a lot of concepts we've learned in previous modules, but applied it to CIs and beta coefficients.
> The extra credit function was pretty challenging to make, but with the help of the boot package & this website: https://cran.r-project.org/package=boot. 

# Peer Comments 
>You did a great job! I didn't have much to comment, just that you could probably explain your bootstrapping a little bit. 